New results in $\sfrac{k}{n}$ Power-Hours

### 2013-12-27 trunk/powerhour/paper/paper.tex
Remove code duplication in powerhour.sml, oops. Implement another performance improvement that slows it down
Cube rendering, looks terrible
New sampling-based enumeration

@@

@@

Define BMnL, where $n$ is the number of non-filled states. BMML=BM2L.
Find $n$ such that a solo or dual power hour achieves any $k$.

>>>>

% #100000 queue 31 min 16 6059166 states/sec 100000 config/sec
% #200000 queue 20 min 16 8762059 states/sec 200000 config/sec
% #300000 queue 35 min 16 12125162 states/sec 300000 config/sec
% #400000 queue 25 min 16 7613270 states/sec 200000 config/sec
% Total steps 15744259. Took 2101 ms

% There are 16 games before splitting.
% #100000 queue 31 min 16 6059166 states/sec 100000 config/sec
% #200000 queue 20 min 16 8762059 states/sec 200000 config/sec
% #300000 queue 35 min 16 6062581 states/sec 150000 config/sec
% #400000 queue 25 min 16 7613270 states/sec 200000 config/sec
% Wrote 454 possibilities to possible-2.txt
% Total steps 15744259. Took 2162 ms

% Wrote 454 possibilities to possible-2.txt
% Total steps 895743. Took 292 ms

% Wrote 2787 possibilities to possible-5cup-60min-2player.txt
% Total steps 6890640495. Took 8161324 ms

% on metroid
% Wrote 37560 possibilities to possible-3.txt
% Total steps 1393736865. Took 1,545,217 ms

@@

\section{Generalized BMML}

\begin{figure}
\begin{center}
\includegraphics[width=0.90 \linewidth]{soloncups.pdf}
\end{center}\vspace{-0.1in}
\caption{Possible outcomes for BM$n$L with a single player. With no
  cup states, it is only possible to drink nothing. By convention, the
  0\th\ cup is the special ``filled'' state, so it is only possible to
  drink on every turn (60) or never (0). As we add more cup states,
  the number of achievable states strictly increases; with 8 cup states
  we can drink any amount. 7 and 53 drinks are the most difficult to
  achieve, and can only be done with 8 cup states.
}
\label{fig:soloncups}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.90 \linewidth]{composite2playermock.png}
\end{center}\vspace{-0.1in}
\caption{What's achievable for the first two players in a three-player
  generalized BM$n$L game, with $n$ ranging from 1 cup state (darkest)
  to 5 (lightest). TODO WRITEME
% 6 cupstates ran overnight and got here:
% #26186200000 queue 109 min 49 466729 states/sec 796272 config/sec
}
\label{fig:composite2player}
\end{figure}

@@

Define BMnL, where $n$ is the number of non-filled states. BMML=BM2L.
(XXX actually I think it's the total number of states including filled
everywhere but that sentence, right?)  Find $n$ such that a solo or
dual power hour achieves any $k$.

\begin{enumerate}
  \item With one player, we have exact bounds on what is possible in
    the generalized case. With 8 cup states, a single player can
    drink 0--60 shots. Since each player can just play independently,
    this result extends to any number of players in BM8L.
  \item With two players, we know that BM5L (XXX check) does not allow
    all combinations of $\langle k_1, k_2 \rangle$ shots, though BM5L
    can achieve any $\langle k_1, k_2 \rangle$ where $\k_2 \in \{ 0, 1
    \}$. No other $k_2$ can be used universally, though of course many
    other combinations are possible
    (Figure~\ref{fig:compositeplayer2mock}).
  \item Open: Can BM6L achieve all $\langle k_1, k_2 \rangle$?
  \item Open: Can BM7L achieve all $\langle k_1, k_2 \rangle$? Seems
    likely, given how close BM7L is for a single player.
  \item With three players one player can drink any number of shots in
    BMML with two other players helping.
\end{enumerate}
